### 2023-03-12 manuscript.tex
* manuscript.tex: Use shorter implication arrow.
* manuscript.tex: Note on surjection to linear transformation.

\documentclass[12pt, a4paper]{report}
\usepackage{imakeidx}
\usepackage{setspace}
\usepackage[type={CC},modifier={by-sa},version={4.0}]{doclicense}
\usepackage[margin=1in]{geometry}
\usepackage{lua-widow-control}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{unicode-math}
\usepackage[style]{abstract}
\usepackage[style=unified]{biblatex}
\usepackage[style=british]{csquotes}
\usepackage{datetime}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tikz}
\usepackage[linguistics]{forest}
\usepackage{linguex}

@@

\renewcommand{\ExLBr}{(\thechapter.}

@@

>>>>

\documentclass[12pt, a4paper]{report}
\usepackage{imakeidx}
\usepackage{setspace}
\usepackage[type={CC},modifier={by-sa},version={4.0}]{doclicense}
\usepackage[margin=1in]{geometry}
\usepackage{lua-widow-control}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{unicode-math}
\usepackage[style]{abstract}
\usepackage[style=unified]{biblatex}
\usepackage[style=british]{csquotes}
\usepackage{datetime}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{ebproof}
\usepackage{tikz}
\usepackage[linguistics]{forest}
\usepackage{linguex}

@@

\renewcommand{\implies}{\Rightarrow}
\renewcommand{\ExLBr}{(\thechapter.}

@@

Is it then easy to see why it works equally well for linear
representations.  \(\mathit{Assoc}\) is merely used to represent the
presence of tones:

\ex.
\a. \(\text{T}(x) = \exists y\ldotp \mathit{Assoc}(y, x)\)
\b. \(\text{T}'(x) = \exists y\ldotp \mathit{Assoc}'(y, x)\)

This makes it possible to surject the autosegmental transformation
into a linear one:

\ex.
\a. \(\text{T}'(x) \coloneq
\text{T}(x) \lor \text{T}'(\mathit{pred}(x))\)
\b.
\begin{prooftree}
  \hypo{\mathit{Assoc}'(a, x) =
    \mathit{Assoc}(a, x) \lor \mathit{Assoc}'(a, \mathit{pred}(x))}
  \infer1{(\exists y\ldotp \mathit{Assoc}'(y, x)) =
    (\exists y\ldotp \mathit{Assoc}(y, x) \lor
    \mathit{Assoc}'(y, \mathit{pred}(x)))}
  \infer1{(\exists y\ldotp \mathit{Assoc}'(y, x)) =
    ((\exists y\ldotp \mathit{Assoc}(y, x)) \lor
    (\exists y\ldotp \mathit{Assoc}'(y, \mathit{pred}(x))))}
  \infer1{\text{T}'(x) = \text{T}(x) \lor \text{T}'(\mathit{pred}(x))}
\end{prooftree}

The existential introduction reflects the fact that the transformation
only cares about the \textemph{existence} of any term on the tonal
tier that is associated with the input term.
